---
title: "607 Assignment 7 Dylan Gold"
format: html
editor: visual
---

## Approach

In this assignment we have to create our own html and json data from information about books. I will do this manually. Then we import them into R and compare them to each other and determine if they are identical. It seems simple enough to me. We need 3 books one with multiple authors. We also need some extra attributes.

For my books I will choose Sunrise Nights by Jeff Zentner and Brittany Cavallaro, The Lord of the Rings by J. R. R. Tolkien and Neuromancer by William Gibson. For my extra attributes I will have publisher, publication date and genre.

I can get the information on these from wikipedia or amazon.\
The data for these books in title, author(s), publisher, publication date, genre are:\
Sunrise Nights, Jeff Zentne; Brittany Cavallaro, Quill Tree Books, July 9, 2024, Romance\
The Lord of the Rings, J. R. R. Tolkien, Allen & Unwin, July 29 1954, Fantasy\
Neuromancer, William Gibson, Ace Books, July 1, 1984, Science fiction\

I will likely use the R functions dplyr all_equal() or identical() to compare them.

## Codebase

First I will create my files by hand. I will start off with the json data.\
I will follow the format from my approach. Each of the books are stored in an overall list.

The following is a copy of my json I created \
[
    {
      "title":"Sunrise Nights",
      "author":["Jeff Zentne", "Brittany Cavallaro"],
      "publisher":"Quill Tree Books",
      "publication_date":"July 9, 2024",
      "genre":"Romance"
    },
    {
      "title":"The Lord of the Rings",
      "author":["J. R. R. Tolkien"],
      "publisher":"Allen & Unwin",
      "publication_date":"July 29, 1954",
      "genre":"Fantasy"
    },
    {
      "title":"Neuromancer",
      "author":["William Gibson"],
      "publisher":"Ace Books",
      "publication_date":"July 1, 1984",
      "genre":"Science fiction"
    }
]

Now I will also create a html table for the data. The data will follow a similar format  \
I was less familiar with creating raw html because most web development has some framework to help. The key things with an html table are <th></th> for the headers, <tr></tr> for the rows then <td></td> for the cells. \
I actually had to go back for one more thing, <ul></ul> for a list, and <li></li> for a list item


This is the table data:
<table>
  	<tr>
    	<th>title</th>
    	<th>author</th>
    	<th>publisher</th>
	<th>publication_date</th>
	<th>genre</th>
  </tr>
  <tr>
    	<td>Sunrise Nights</td>
    	<td>Jeff Zentne, Brittany Cavallaro</td>
    	<td>Quill Tree Books</td>
	<td>July 9, 2024</td>
	<td>Romance</td>
  </tr>
  <tr>
    	<td>The Lord of the Rings</td>
    	<td>J. R. R. Tolkien</td>
    	<td>Allen & Unwin</td>
	<td>July 29, 1954</td>
	<td>Fantasy</td>
  </tr>
  <tr>
    	<td>Neuromancer</td>
    	<td>William Gibson</td>
    	<td>Ace Books</td>
	<td>July 1, 1984</td>
	<td>Science fiction</td>
  </tr>
</table>

First I put them into my github directory. \

I also need some libraries to make this easier, rvest for the html and jsonlite for the json.
```{r warning=FALSE}
library(rvest)
library(jsonlite)

```

Now we can bring them into R, to bring the html into R I will use a package called rvest
```{r, warning=FALSE}
library(rvest)
html_url <- "https://raw.githubusercontent.com/DylanGoldJ/607-Assignment-5/refs/heads/main/books.html"

html_books <- read_html(html_url) %>% html_table()
```

Now the json file, I will use jsonlite for this
```{r}
json_url <- "https://raw.githubusercontent.com/DylanGoldJ/607-Assignment-5/refs/heads/main/books.json"

json_books <- fromJSON(json_url)
```


























